The role of motor inhibition during covert speech production

### 2021-10-29 manuscript.tex
incorporating final feedback

%\setcitestyle{square} % for Physics and Applied Mathematics and Statistics articles
% \usepackage{url,hyperref,lineno,microtype,subcaption}
\usepackage{url,hyperref,lineno,microtype}
\usepackage[onehalfspacing]{setspace}

@@

% Leave a blank line between paragraphs instead of using \\

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Nalborczyk {et al.}} % use et al only if is more than 1 author
\def\Authors{Ladislas Nalborczyk\,$^{1,2,*}$, Ursula Debarnot\,$^{3,4}$, Marieke Longcamp\,$^{2}$, Aymeric Guillot\,$^{3,4}$, and F.-Xavier Alario\,$^{1}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$Aix Marseille Univ, CNRS, LPC, Marseille, France \\
$^{2}$Aix Marseille Univ, CNRS, LNC, Marseille, France \\
$^{3}$Inter-University Laboratory of Human Movement Biology-EA 7424, University of Lyon, University Claude Bernard Lyon 1, Villeurbanne, France \\
$^{4}$Institut Universitaire de France, Paris, France}
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Ladislas Nalborczyk}
\def\corrEmail{ladislas.nalborczyk@univ-amu.fr}

@@

% A significant consequence of this hypothesis is that the sensory experience of covert speech would be shaped by sensorimotor interactions with the environment. However, the precise computations required by these internal models and their neural implementation remain unclear. Moreover,

@@

\tiny
 \keyFont{\section{Keywords:} covert speech, inner speech, motor imagery, motor simulation, motor control, motor inhibition} % All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\end{abstract}

@@

% \cite{diesburg_pause-then-cancel_2021} proposed a functional dissociation between the pre-SMA and the rIFC in a two-stage "pause-then-cancel" model of action inhibition. In their model, they suggest that the pre-SMA would be involved in (globally) pausing the action whereas the rIFC would be involved in selectively cancelling (resetting) motor commands. Whether this functional dissociation is preserved in motor imagery and covert speech remains an open question.

% It has been suggested that the primary motor cortex would be "bypassed" during covert speech  \citep[e.g.,][]{tian_mental_2012, tian_effect_2013, tian_mental_2016} or that motor commands would be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018, grandchamp_condialint_2019}

Whether motor commands are emitted and subsequently inhibited during covert speech production is an issue that has been debated \citep[e.g.,][]{geva_inner_2018}. It has been suggested that during covert speech production, motor commands would be "simply specified in sub-threshold way, requiring no active inhibition" \citep{geva_inner_2018}. Alternatively, during covert speech production, motor commands may be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018, grandchamp_condialint_2019}. However, stating that covert speech (or motor imagery, more generally) only involves subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned or monitored" \citep[see also][]{scheil_motor_2018}. In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level. What cognitive and neural mechanisms operate to maintain this activity under the threshold? In this section, we provided empirical arguments in favour of the "active inhibition hypothesis". Proponents of the "subliminal level hypothesis" need to clarify how this activity is maintained at a subthreshold level during covert speech production, thus preventing execution.

% \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}... \cite{ganos_action_2014} have showed that the behavioural performance during a stop-signal reaction-time task was similar across Tourette patients and healthy controls...

The putative involvement and functional role of inhibitory mechanisms during covert speech could be assessed in several ways. First, it could be assessed by experimentally manipulating the activity of the inhibitory network responsible for preventing execution during motor imagery. For instance, transcranial magnetic stimulation (TMS) could be used to interrupt these inhibitory mechanisms and thus facilitate execution during motor imagery. Second, the role of inhibitory mechanisms during covert verbal actions could be examined in populations with well-identified inhibitory deficits. For instance, Tourette syndrome is a childhood-onset neurological disorder affecting approximately 1\% of children and characterised by chronic motor and phonic tics \citep{jackson_inhibition_2015}. Verbal tics can consist of repeating sounds, words, or utterances (palilalia), producing inappropriate or obscene utterances (coprolalia), or the repetition of another’s words (echolalia). In their review, \cite{jackson_inhibition_2015} suggested that increased control over motor outputs, acquired by repeatedly trying to suppress tics, is brought by local increases in GABAergic "tonic" inhibition within regions such as the SMA, leading to localised reductions in the gain of motor excitability. For these reasons, comparing the neural implementation of inhibitory mechanisms during covert speech in patients with Tourette syndrome and healthy controls may shed light on the role and flexibility of these mechanisms.

@@

% In other words, Vygotsky observed that egocentric speech tends to be internalised during child development.

\cite{watson_psychology_1919} suggested that thought was rooted in overt speech. In his terminology, thought referred to covert speech. Hence, his view was that covert speech matures from overt speech. \cite{vygotsky_thought_1934} further formulated the idea that covert speech is internalised during childhood from private egocentric speech, that is, from self-addressed overt speech. \cite{fernyhough_alien_2004} extended these ideas by proposing four levels of internalisation: external dialogue, private speech, expanded inner speech, and condensed inner speech. These levels represent stages of development but also define movements between levels, that is, how we go from overt to covert speech and conversely. The level at which speech is expressed may depend on inhibitory control applied at different levels in the production flow, such as the formulation or the articulatory planning level \citep{grandchamp_condialint_2019}. Therefore, producing speech covertly crucially depends on successfully inhibiting speech production at several levels.

@@

% Essentially, learning to play the piano can be said to consist in learning to produce and coordinate complex and fine-grained motor sequences that in turn produce multisensory (e.g., kinaesthetic, auditory, visual) feedback to the agent producing of the action. Therefore

@@

% in the light of the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}.

The dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016} describes two neural pathways that may provide the auditory content of covert speech. First, the simulation-estimation prediction stream implements a motor-to-sensory transformation via motor simulation, that is, by simulating speech movements and the perceptual changes that would be associated with these movements \citep[see also][for a similar proposal]{loevenbruck_cognitive_2018}. This stream includes cerebral areas involved in speech motor preparation such as the supplementary motor area, the inferior frontal gyrus, the premotor cortex and the insula, as well as brain areas involved in somatosensory estimation and perception such as primary and secondary somatosensory regions, the parietal operculum, and the supramarginal gyrus \citep{tian_mental_2016}. Second, the memory-retrieval prediction stream may be used to provide auditory percepts by "reconstructing stored perceptual information in modality-specific cortices" \citep{tian_mental_2016}. This mechanism provides sensory percepts without the need for computing the predicted sensory consequences of (non executed) motor commands. Auditory percepts may be retrieved from various memory sources, relying (amongst others) on the hippocampal structures \citep{tian_mental_2016}. Auditory percepts may also be retrieved from lexical and semantic information stored in semantic networks, including frontal, temporal, and parietal regions \citep[for more details, see][]{tian_mental_2016}.

% In other words, sensory percepts would be generated by activating sensory-specific cortices from object properties stored in long-term memory.

% \footnote{This distinction shares similarities with the distinction between the prediction-by-simulation or prediction-by-association mechanisms in speech production and comprehension suggested by \cite{pickering_integrated_2013}.}

@@

% where motor-to-sensory mappings are partially or completely retrieved from memory, instead of being computed again every time.

% \vspace{5mm}

@@

% Crucially, different forms of covert speech, varying in condensation, dialogicality, or intentionality, may require inhibitory control to a different extent.

@@

% All financial, commercial or other relationships that might be perceived by the academic community as representing a potential conflict of interest must be disclosed. If no such relationship exists, authors will be asked to confirm the following statement:

@@

% Please see the availability of data guidelines for more information, at https://www.frontiersin.org/about/author-guidelines#AvailabilityofData

\bibliographystyle{template/frontiersinSCNS_ENG_HUMS} % for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
%\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
% \bibliography{test}
\bibliography{bibliography/covert_verbal_actions}

%%% Make sure to upload the bib file along with the tex file and PDF
%%% Please see the test.bib file for some examples of references

>>>>

% \usepackage{url,hyperref,lineno,microtype,subcaption}
\usepackage{url,hyperref,lineno,microtype}
\usepackage[onehalfspacing]{setspace}

@@

% Leave a blank line between paragraphs instead of using \\
\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Nalborczyk {et al.}} % use et al only if is more than 1 author
\def\Authors{Ladislas Nalborczyk\,$^{1,2,*}$, Ursula Debarnot\,$^{3,4}$, Marieke Longcamp\,$^{2}$, Aymeric Guillot\,$^{3,4}$, and F.-Xavier Alario\,$^{1}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$Aix Marseille Univ, CNRS, LPC, Marseille, France \\
$^{2}$Aix Marseille Univ, CNRS, LNC, Marseille, France \\
$^{3}$Inter-University Laboratory of Human Movement Biology-EA 7424, University of Lyon, University Claude Bernard Lyon 1, Villeurbanne, France \\
$^{4}$Institut Universitaire de France, Paris, France}
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Ladislas Nalborczyk}
\def\corrEmail{ladislas.nalborczyk@univ-amu.fr}

@@

@@

\tiny
 \keyFont{\section{Keywords:} covert speech, inner speech, motor imagery, motor simulation, motor control, motor inhibition} % All article types: you may provide up to 8 keywords; at least 5 are mandatory.

\end{abstract}

@@

Whether motor commands are emitted and subsequently inhibited during covert speech production is an issue that has been debated \citep[e.g.,][]{geva_inner_2018}. It has been suggested that during covert speech production, motor commands would be "simply specified in sub-threshold way, requiring no active inhibition" \citep{geva_inner_2018}. Alternatively, motor commands may be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018, grandchamp_condialint_2019}. However, stating that covert speech (or motor imagery, more generally) only involves subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned or monitored" \citep[see also][]{scheil_motor_2018}. In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level. What cognitive and neural mechanisms operate to maintain this activity under the threshold? In this section, we provided empirical arguments in favour of the "active inhibition hypothesis". Proponents of the "subliminal level hypothesis" need to clarify how this activity is maintained at a subthreshold level during covert speech production, thus preventing execution.

The putative involvement and functional role of inhibitory mechanisms during covert speech could be assessed in several ways. First, it could be assessed by experimentally manipulating the activity of the inhibitory network responsible for preventing execution during motor imagery. For instance, transcranial magnetic stimulation (TMS) could be used to interrupt these inhibitory mechanisms and thus facilitate execution during motor imagery. Second, the role of inhibitory mechanisms during covert verbal actions could be examined in populations with well-identified inhibitory deficits. For instance, Tourette syndrome is a childhood-onset neurological disorder affecting approximately 1\% of children and characterised by chronic motor and phonic tics \citep{jackson_inhibition_2015}. Verbal tics can consist of repeating sounds, words, or utterances (palilalia), producing inappropriate or obscene utterances (coprolalia), or the repetition of another’s words (echolalia). In their review, \cite{jackson_inhibition_2015} suggested that increased control over motor outputs, acquired by repeatedly trying to suppress tics, is brought about by local increases in GABAergic "tonic" inhibition within regions such as the SMA, leading to localised reductions in the gain of motor excitability. For these reasons, comparing the neural implementation of inhibitory mechanisms during covert speech in patients with Tourette syndrome and healthy controls may shed light on the role and flexibility of these mechanisms.

@@

\cite{watson_psychology_1919} suggested that thought was rooted in overt speech. In his terminology, thought referred to covert speech. Hence, his view was that covert speech matures from overt speech. \cite{vygotsky_thought_1934} further formulated the idea that covert speech is internalised during childhood from private egocentric speech, that is, from self-addressed overt speech. \cite{fernyhough_alien_2004} extended these ideas by proposing four levels of internalisation: external dialogue, private speech, expanded inner speech, and condensed inner speech. These levels represent stages of development but also define movements between levels, that is, how a speaker may go from overt to covert speech and conversely. The level at which speech is expressed may depend on inhibitory control applied at different levels in the production flow, such as the formulation or the articulatory planning level \citep{grandchamp_condialint_2019}. Therefore, producing covert speech crucially depends on successfully inhibiting speech production at several levels.

@@

@@

The dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016} describes two neural pathways that may provide the auditory content of covert speech. First, the simulation-estimation prediction stream implements a motor-to-sensory transformation via motor simulation, that is, by simulating speech movements and the perceptual changes that would be associated with these movements \citep[see also][for a similar proposal]{loevenbruck_cognitive_2018}. This stream includes cerebral areas involved in speech motor preparation such as the supplementary motor area, the inferior frontal gyrus, the premotor cortex and the insula, as well as brain areas involved in somatosensory estimation and perception such as primary and secondary somatosensory regions, the parietal operculum, and the supramarginal gyrus \citep{tian_mental_2016}. Second, the memory-retrieval prediction stream may be used to provide auditory percepts by "reconstructing stored perceptual information in modality-specific cortices" \citep{tian_mental_2016}. This mechanism provides sensory percepts without the need for computing the predicted sensory consequences of (non executed) motor commands. Auditory percepts may be retrieved from various memory sources, relying (amongst others) on the hippocampal structures \citep{tian_mental_2016}. Auditory percepts may also be retrieved from a broad fronto-temporo-parietal lexico-semantic network \citep[for more details, see][]{tian_mental_2016}.

% Auditory percepts may also be retrieved from lexical and semantic information stored in semantic networks, including frontal, temporal, and parietal regions \citep[for more details, see][]{tian_mental_2016}.

@@

@@

@@

@@

\bibliographystyle{template/frontiersinSCNS_ENG_HUMS}
\bibliography{bibliography/covert_verbal_actions}
